\section{Theory}\label{sec:Theory}
In this Chapter a brief introduction to the standard model of particle physics (SM) and its important aspects regarding cosmic rays is given.

\subsection{The Standard Model of Particle Physics}
The SM \cite{griffiths} is the theory that describes all known fundamental interactions except gravity. These are the strong, weak, and electromagnetic interactions. It also contains and classifies all known elementary particles, which are divided into fermions and bosons.
Fermions have spin $1/2$ and can be further divided into quarks and leptons.
There are six quarks called \textit{up} (u), \textit{down} (d), \textit{charm} (c), \textit{strange} (s), \textit{top} (t) and \textit{bottom} (b).
These fall into three generations
\begin{equation*}
  \binom{u}{d},\binom{c}{s},\binom{t}{b}.
\end{equation*}
The \textit{up-type} quarks u, c and t have an electric charge $Q = \frac{2}{3}$ while the \textit{down-type} quarks d, s and b have an electric charge $Q = - \frac{1}{3}$.
Additionally, quarks come in three different color charges red, green, and blue and their respective anticolours.

The six leptons are also categorized into three generations consisting of one of the charged leptons electron, muon and tau and their respective left-handed neutrino:
\begin{equation*}
  \binom{e^-}{\nu_e},\binom{\mu^-}{\nu_\mu},\binom{\tau^-}{\nu_\tau}.
\end{equation*}
The electric charge of the charged leptons is $\num{-1}$ while neutrinos are neutral.

Each class of fermions is divided into generations since they show the same physical behaviour, but have a higher mass in comparison to lower generations.\\

Bosons have an integer spin and are distinguished between gauge bosons and the Higgs boson.
Gauge bosons have spin $1$ and are mediators of the fundamental interactions. Photons mediate the electromagnetic interaction and couple to electric charge, gluons the mediators of the strong interaction and couple to color charge and the $W^{\pm}$ and the $Z^0$ bosons mediate the weak interaction.

The Higgs boson has a spin $0$ and does not act as a mediator. It is the newest addition to the SM and was discovered 2012 at the LHC\cite{ATLAS:2012yve}.

\subsection{Cosmic Rays}
The earth is constantly bombarded with highly energetic particles. These cosmic rays (CR) mostly consist of protons ($\approx \SI{89}{\percent}$) and $\alpha$-particles ($\approx \SI{10}{\percent}$). The remaining percent are contributions from heavier nuclei. This radiation can achieve energies up to $10^{20}\,\si{\electronvolt}$ and the energy spectrum can approximately be described by a power law
\begin{equation}
  \frac{\mathrm{d}\Phi}{\mathrm{d}E} = \Phi_0 E^{\gamma},
\end{equation}
where $\gamma \approx - 2.7$ is the spectral index.

Due to the electric charge of the CR particles they are deflected in the galactic and extragalactic magnetic fields resulting in an isotropic flux from all directions.\\

The muons and neutrinos detected by IceCube can either come from astrophysical sources directly or be produced in atmospheric interactions of primary CRs. The latter can be separated into prompt and conventional muons and neutrinos regarding their energetic spectrum. Conventional muons and neutrinos come from pions and kaons formed when the primary CRs interact with the earth's atmosphere. Due to their comparatively large lifetimes these particles lose energy before decaying into muons and neutrinos resulting in a energy spectrum $\propto E^{-3.7}$.

Prompt muons and neutrinos are produced in the decay of $D$ mesons and $\Lambda_c$ baryons, which can be produced at high energies. These have very short lifetimes and therefore do not lose any energy before decaying, leading to an energy spectrum $\propto E^{-2.7}$ for the muons and neutrinos.

It is expected that cosmological sources of accelerated hadrons also emit photons and neutrinos. These are not deflected in the galactic and extragalactic magnetic fields due to their lack of electric charge. Photons are significantly affected by absorption and emission processes though, leading to a loss of the information about their source directions. Neutrinos on the other hand are able to pass through optically dense media due to their small cross section. Therefore the arrival directions of neutrinos point back to their sources.

Under the assumption of shock acceleration \cite{Fermi}, a spectral index $\gamma \approx 2$ is expected.
