\section{Discussion}
\label{sec:Diskussion}
Both for the simulated data in \autoref{f2}, as well as for the real data in \autoref{f4} a clear peak is visible at the B-mass in the
mass spectrum. The peak produced by real data is much wider since the simulated dataset is not distorted by the detector. Additionally
more Background events are visible in the real data since the simulated data does not contain background events. This is especially
prevelent in the lower sideband region of the signal. This effect in the lower sideband could be a result of a misidentification of final state
particles as kaons in calculation of the energy. \\
The global \textit{CP}-asymmetry of $A_\textit{CP} = 0.05 \pm 0.01 (stat) \pm 0.01 (prod)$ does cross the threshhold of evidence with $3.98 \sigma$
but is not an observation. The significance
could possibly be reduced more if effects like the detector resolution are taken into account but this is not investigated further. \\
In the generated Dalitz plots in figure \ref{f5} and \ref{f6} three charm resonances are identified and removed. The cuts for the
removal of the resonances have been determined by eye and could possibly be improved to achieve better results.
in figure \ref{f7} the bin
\begin{align*}
    1.99 \cdot 10^{7} \, \si{\mega\eV\squared} &\lesssim M(R_\text{max})^2 \lesssim 2.33 \cdot 10^{7} \, \si{\mega\eV\squared} \\
    0.64 \cdot 10^{7} \, \si{\mega\eV\squared} &\lesssim M(R_\text{min})^2 \lesssim 0.98 \cdot 10^{7} \, \si{\mega\eV\squared}
\end{align*}
has a very high significance of $100 \sigma$ but is disregarded in the analysis since it only contains two $B^+$-candidates and no $B^-$-candidates.
In the area investigated in the analysis a local \textit{CP}-asymmetry of $A_\textit{CP} = -0.15  \pm 0.01  (stat)  \pm 0.01(prod)$ could be observed
with $8.73 \sigma$, crossing the threshold of observation. The significance could possibly improved further if other bin- sizes and shapes are
investigated. This asymmetry is visible in the comparism of the mass spectra of $B^+$- and $B^-$-candidates in figure \ref{f8} where more
$B^+$-candidates are observed.
