\section{Discussion}
\label{sec:Diskussion}
Comparing simulated data with measured data shows a much sharper peak at the $B$ mass in simulated data.
This is because detector resolution effects were not simulated in this data set.
These effects would smear out the distribution of events as seen in the measured data set.
Connected to that is the position of the cut of the particle identification variables.
It shows that harder cuts would cause a significant signal loss.
In this analysis no special method was used to determine these cuts so a detailed analysis of this might cause more accuracy.

The global $C\!P$ asymmetry shows a significance of nearly $4\,\sigma$.
This is an evidence on global $C\!P$ asymmetry but not an observation since the significance is smaller than $5\,\sigma$.
In this analysis the only source of systematic uncertainties is production asymmetry.
Including effects like detector effects and uncertainties in luminosity might give more accurate results.
The LHCb paper \cite{paper} used the same data set and included systematic uncertainties in trigger asymmetrie and acceptance correction.

The Dalitz plots showed charmonium resonances in the data set.
To make a more pure set these resonances were cut out at their respective masses.

Local $C\!P$ asymmetry shows a significance of $7.77\,\sigma$ yielding an observation of local $C\!P$ asymmetry.
This significance includes the statistical uncertainty and a $1\,\%$ uncertainty from production asymmetry.
The location of this local $C\!P$ asymmetry was delivered from the binned Dalitz plot.
More analyses on binning and optimal location could lead to improvement of this results.
To increase the accuracy the systematic uncertainies mentioned before should be taken into account as well.

Comparing the $B^+$ and $B^-$ shows a clearly larger amount of $B^-$ events.

In this analysis only the decay of a $B$ meson into three kaons is studied since the background of this decay is the lowest.
Decays with pions in the final state have larger backgrounds.
Analyzing these decay channels might indicate more information on $C\!P$ violation and give more statistics due to the higher branching ratio.
